
---
title: "Exercises on String Manipulation and Custom Pig Latin"
output: github_document
---

# Exercise 1: Word Frequency Analysis in "Pride and Prejudice"

## Introduction

This exercise involves analyzing a text from Jane Austen's "Pride and Prejudice" to identify the most common words, excluding stopwords.

## Load Necessary Packages

References:

* janeaustenr Package: Accessing Jane Austen's books.
https://github.com/juliasilge/janeaustenr

* stopwords Package: For a predefined list of stop words.
https://cran.r-project.org/web/packages/stopwords/readme/README.html

```{r setup, include=TRUE}
# Load the libraries
library(janeaustenr)
library(tidyverse)
library(tidytext)
library(stopwords)
```

## Load and Prepare the Text

```{r}
# Load "Pride and Prejudice" text
book_text <- austen_books() %>%
  filter(book == "Pride & Prejudice") %>%
  select(text)

# Display the first few lines
head(book_text)
```

## Tokenize Text and Remove Stop Words

```{r}
# Define stop words using the stopwords package (English)
stop_words_custom <- stopwords::stopwords("en")

# Tokenize the text and remove stop words
tidy_words <- book_text %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words_custom) %>%
  filter(str_detect(word, "^[a-z]+$"))  # Keep only words with letters

# View the tidy words
head(tidy_words)
```

## Count Word Frequencies

```{r}
# Count the most common words
word_counts <- tidy_words %>%
  count(word, sort = TRUE)

# View the top 20 most common words
head(word_counts, 20)
```

## Plot the Most Common Words

```{r plot, echo=TRUE}
# Select the top 20 words
top_words <- word_counts %>%
  top_n(20, n) %>%
  arrange(desc(n))

# Plot
ggplot(top_words, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Most Common Words in 'Pride and Prejudice'",
       x = "Words",
       y = "Frequency") +
  theme_minimal()
```

# Exercise 2: Custom Pig Latin Converter

## Function Definition

```{r pig-latin-function, include=TRUE}
# Load necessary library for string manipulation
library(stringr)

#' Convert a Word to Custom Pig Latin
#'
#' This function converts English words to a customized version of Pig Latin by applying specific rearrangement and addition rules.
#'
#' Rearrangement Rules:
#' - Consonant Start: If the word begins with a consonant or a consonant cluster, move the initial consonant(s) to the end of the word.
#' - Vowel Start: If the word begins with a vowel, move the last consonant in the word to the beginning.
#' - No Vowels: If the word contains no vowels, leave it unchanged in the rearrangement phase.
#'
#' Addition Rule:
#' - Append "bee" to the end of the rearranged word.
#'
#' @param word A single word (character string) to be converted. Must contain only alphabetic characters.
#' @return A character string representing the word in customized Pig Latin.
#' @examples
#' custom_pig_latin("hello")    # "ellohbee"
#' custom_pig_latin("apple")    # "lappebee"
#' custom_pig_latin("string")   # "ingstrbee"
#' custom_pig_latin("orange")   # "goranebee"
#' custom_pig_latin("rhythm")   # "rhythmbee"
#' @export
custom_pig_latin <- function(word) {
  # Input validation
  if (!is.character(word)) {
    stop("Input must be a character string.")
  }
  
  if (length(word) != 1) {
    stop("Input must be a single word.")
  }
  
  if (!str_detect(word, "^[A-Za-z]+$")) {
    stop("Input must contain only alphabetic characters.")
  }
  
  # Define vowels
  vowels <- c("a", "e", "i", "o", "u")
  
  # Convert word to lowercase for processing
  lower_word <- tolower(word)
  
  # Function to identify the initial consonant cluster at the start
  get_initial_consonant_cluster <- function(w) {
    first_vowel_pos <- str_locate(w, "[aeiou]")[1, "start"]
    if (is.na(first_vowel_pos)) {
      # No vowels, entire word is consonant cluster
      return(w)
    } else if (first_vowel_pos == 1) {
      # Starts with vowel
      return("")
    } else {
      # Return the initial consonant cluster
      return(str_sub(w, 1, first_vowel_pos - 1))
    }
  }
  
  # Function to identify the last consonant in the word
  get_last_consonant <- function(w) {
    # Find all consonants in the word
    consonants <- str_extract_all(w, "[bcdfghjklmnpqrstvwxyz]")[[1]]
    if (length(consonants) == 0) {
      return("")
    } else {
      # Find the last consonant
      last_consonant <- tail(consonants, n = 1)
      return(last_consonant)
    }
  }
  
  # Function to replace the last occurrence of a pattern in a string
  replace_last_occurrence <- function(string, pattern, replacement) {
    # Create a regex pattern that matches the last occurrence of the pattern
    # Uses a negative lookahead to ensure it's the last occurrence
    regex_pattern <- paste0("(", pattern, ")(?!.*", pattern, ")")
    
    # Perform the replacement
    str_replace(string, regex_pattern, replacement)
  }
  
  # Check if the first letter is a vowel
  first_letter <- str_sub(lower_word, 1, 1)
  
  if (first_letter %in% vowels) {
    # Vowel start: move the last consonant to the beginning
    last_consonant <- get_last_consonant(lower_word)
    if (last_consonant == "") {
      # No consonants, leave the word as is
      rearranged_word <- lower_word
    } else {
      # Remove the last consonant from its position using the replacement logic
      rearranged_word <- replace_last_occurrence(lower_word, fixed(last_consonant), "")
      # Prepend the last consonant
      rearranged_word <- str_c(last_consonant, rearranged_word)
    }
  } else {
    # Consonant start: move the initial consonant cluster to the end
    initial_consonant_cluster <- get_initial_consonant_cluster(lower_word)
    if (initial_consonant_cluster == "") {
      rearranged_word <- lower_word
    } else {
      # Remove the initial consonant cluster
      rearranged_word <- str_replace(lower_word, fixed(initial_consonant_cluster), "")
      # Append the initial consonant cluster to the end
      rearranged_word <- str_c(rearranged_word, initial_consonant_cluster)
    }
  }
  
  # Addition component: append "bee"
  pig_latin_word <- str_c(rearranged_word, "bee")
  
  # Preserve original casing: if the original word starts with an uppercase letter, capitalize the first letter
  if (str_detect(word, "^[A-Z]")) {
    pig_latin_word <- str_to_title(pig_latin_word)
  }
  
  return(pig_latin_word)
}
```

## Examples

```{r pig-latin-examples}
# Example 1: Word starts with a consonant
custom_pig_latin("hello")   # Expected Output: "ellohbee"

# Example 2: Word starts with a vowel
custom_pig_latin("apple")   # Expected Output: "lappebee"

# Example 3: Word with consonant cluster
custom_pig_latin("string")  # Expected Output: "ingstrbee"

# Example 4: Word starts with a vowel and has multiple consonants
custom_pig_latin("orange")  # Expected Output: "goranebee"

# Example 5: Word with no vowels
custom_pig_latin("rhythm")  # Expected Output: "rhythmbee"

# Example 6: Capitalized word
custom_pig_latin("Hello")   # Expected Output: "Ellohbee"
```

## Tests

```{r pig-latin-tests,error=TRUE}
# Load necessary libraries
library(testthat)

test_that("custom_pig_latin returns correct Pig Latin conversion", {
  # Test 1: Word starts with a consonant
  expect_equal(custom_pig_latin("hello"), "ellohbee")
  
  # Test 2: Word starts with a vowel
  expect_equal(custom_pig_latin("apple"), "lappebee")
  
  # Test 3: Word with consonant cluster
  expect_equal(custom_pig_latin("string"), "ingstrbee")
  
  # Test 4: Word with no vowels
  expect_equal(custom_pig_latin("rhythm"), "rhythmbee")
  
  # Test 5: Capitalized word
  expect_equal(custom_pig_latin("Hello"), "Ellohbee")
})

test_that("custom_pig_latin output ends with 'bee'", {
  # Example words
  words <- c("hello", "apple", "string", "orange", "rhythm", "Umbrella")
  
  # Apply the function
  transformed_words <- sapply(words, custom_pig_latin)
  
  # Check that each transformed word ends with "bee"
  expect_true(all(str_ends(transformed_words, "bee")))
})

test_that("custom_pig_latin handles invalid inputs appropriately", {
  # Test with numeric input
  expect_error(custom_pig_latin(123), "Input must be a character string.")
  
  # Test with multiple words
  expect_error(custom_pig_latin(c("hello", "world")), "Input must be a single word.")
  
  # Test with non-alphabetic characters
  expect_error(custom_pig_latin("hello123"), "Input must contain only alphabetic characters.")
  
  expect_error(custom_pig_latin("hello-world"), "Input must contain only alphabetic characters.")
  
  # Test with empty string
  expect_error(custom_pig_latin(""), "Input must contain only alphabetic characters.")
})
```
